---
title: "R-Code"
author: "Elisa Bayoumi"
date: "12/10/2020"
output: pdf_document
---

```{r, packages, eval=FALSE}

library(tidyverse)
library(rtweet)
library(lubridate)
library(ggplot2)
library(tm)
library(wordcloud)
```


```{r, Use API, eval = FALSE}
Trump_Tweets_1000 <- get_timeline(
  user = "realdonaldtrump",
  n = 1000,
  include_rts = TRUE,
  retryonratelimit = TRUE)
#New element to preserve the 997 entries
trump_tweets_997 <- Trump_Tweets_1000
```

```{r, flagged tweet URLs}
#Broken it into parts because it runs more easily and helps find bugs
flagged_url <- c(
"https://twitter.com/realDonaldTrump/status/1336847458836631553",
"https://twitter.com/realDonaldTrump/status/1336844470994821126",
"https://twitter.com/realDonaldTrump/status/1336811823232921600",
"https://twitter.com/realDonaldTrump/status/1336730906107768842",
"https://twitter.com/realDonaldTrump/status/1336691515398250498",
"https://twitter.com/realDonaldTrump/status/1336680803682693126",
"https://twitter.com/realDonaldTrump/status/1336680713568071681",
"https://twitter.com/realDonaldTrump/status/1336666810742149120",
"https://twitter.com/realDonaldTrump/status/1336407510069161988",
"https://twitter.com/realDonaldTrump/status/1336322408970559495",
"https://twitter.com/realDonaldTrump/status/1336177638528983041",
"https://twitter.com/realDonaldTrump/status/1336148836495069185",
"https://twitter.com/realDonaldTrump/status/1336114633485266944",
"https://twitter.com/realDonaldTrump/status/1335971721262796801", "https://twitter.com/realDonaldTrump/status/1335761079750766592", "https://twitter.com/realDonaldTrump/status/1335739297459265537", "https://twitter.com/realDonaldTrump/status/1335775535717289984", "https://twitter.com/realDonaldTrump/status/1335775501739307009", "https://twitter.com/realDonaldTrump/status/1335775434546548737", "https://twitter.com/realDonaldTrump/status/1335761079750766592", "https://twitter.com/realDonaldTrump/status/1335739297459265537", "https://twitter.com/realDonaldTrump/status/1335736235239804928", "https://twitter.com/realDonaldTrump/status/1335713485020401671", "https://twitter.com/ScottAdamsSays/status/1335620794861252608", "https://twitter.com/realDonaldTrump/status/1335663612954898434", "https://twitter.com/TeamTrump/status/1335377409584017409", "https://twitter.com/OANN/status/1334590527451250688")
flagged_url <- c(flagged_url, "https://twitter.com/gatewaypundit/status/1334593386679050243", "https://twitter.com/christina_bobb/status/1334870568349405184", "https://twitter.com/MarkFinchem/status/1334890192327618560", "https://twitter.com/RudyGiuliani/status/1334959988306042882", "https://twitter.com/realDonaldTrump/status/1335462704006492160", "https://twitter.com/christina_bobb/status/1335258070633615361", "https://twitter.com/realDonaldTrump/status/1335460410267488261", "https://twitter.com/realDonaldTrump/status/1335413770139549697", "https://twitter.com/realDonaldTrump/status/1335406436247998464", "https://twitter.com/realDonaldTrump/status/1335052022530379776", "https://twitter.com/realDonaldTrump/status/1334994862299602947", "https://twitter.com/realDonaldTrump/status/1335057724485275656", "https://twitter.com/realDonaldTrump/status/1335057703568355330", "https://twitter.com/realDonaldTrump/status/1335052022530379776", "https://twitter.com/realDonaldTrump/status/1335032599283109890", "https://twitter.com/realDonaldTrump/status/1334994862299602947", "https://twitter.com/realDonaldTrump/status/1334949289160740866", "https://twitter.com/realDonaldTrump/status/1334858852337070083", "https://twitter.com/realDonaldTrump/status/1334848556176379907", "https://twitter.com/realDonaldTrump/status/1334670866051981312", "https://twitter.com/realDonaldTrump/status/1334617669316845580", "https://twitter.com/realDonaldTrump/status/1334611537688809472", "https://twitter.com/realDonaldTrump/status/1334606278388277253", "https://twitter.com/realDonaldTrump/status/1334573529107460096") 
flagged_url <- c(flagged_url, "https://twitter.com/TeamTrump/status/1334569329334083586", "https://twitter.com/TeamTrump/status/1334566301205925889", "https://twitter.com/realDonaldTrump/status/1334351957113311233", "https://twitter.com/realDonaldTrump/status/1334327894844248070", "https://twitter.com/realDonaldTrump/status/1334327603340201984", "https://twitter.com/realDonaldTrump/status/1334327470972137474", "https://twitter.com/realDonaldTrump/status/1334327204847775744", "https://twitter.com/realDonaldTrump/status/1334326746615865344", "https://twitter.com/realDonaldTrump/status/1334303260279234562", "https://twitter.com/realDonaldTrump/status/1334282156349267970", "https://twitter.com/AZGOP/status/1334165432161374209", "https://twitter.com/realDonaldTrump/status/1334240039639937026", "https://twitter.com/realDonaldTrump/status/1334167828035989506", "https://twitter.com/realDonaldTrump/status/1334167769575796739", "https://twitter.com/realDonaldTrump/status/1334001184298905601", "https://twitter.com/realDonaldTrump/status/1334155285909409801", "https://twitter.com/realDonaldTrump/status/1334001184298905601", "https://twitter.com/realDonaldTrump/status/1333988969785257984", "https://twitter.com/realDonaldTrump/status/1333975991518187521", "https://twitter.com/LouDobbs/status/1333912209311805446", "https://twitter.com/realDonaldTrump/status/1333888306178908163", "https://twitter.com/realDonaldTrump/status/1333856259662077954", "https://twitter.com/realDonaldTrump/status/1333773762374807553", "https://twitter.com/realDonaldTrump/status/1333772740483026944", "https://twitter.com/realDonaldTrump/status/1333771923214491648", "https://twitter.com/realDonaldTrump/status/1333771177005867008", "https://twitter.com/iheartmindy/status/1329901868315623424")
flagged_url <- c(flagged_url, "https://twitter.com/KamVTV/status/1333479464089628679", "https://twitter.com/thebradfordfile/status/1333562182232104965", "https://twitter.com/realDonaldTrump/status/1333615151904395264", "https://twitter.com/realDonaldTrump/status/1333558773152161793", "https://twitter.com/realDonaldTrump/status/1333558147512999938", "https://twitter.com/realDonaldTrump/status/1333464453778706433", "https://twitter.com/realDonaldTrump/status/1333410418119864320", "https://twitter.com/realDonaldTrump/status/1333410419554344964", "https://twitter.com/realDonaldTrump/status/1333244506871918599", "https://twitter.com/LizRNC/status/1333033172783738880", "https://twitter.com/realDonaldTrump/status/1333243285389914112", "https://twitter.com/realDonaldTrump/status/1333215466022727686", "https://twitter.com/realDonaldTrump/status/1333207778643628032", "https://twitter.com/realDonaldTrump/status/1333084358446551042", "https://twitter.com/realDonaldTrump/status/1333084321863888896", "https://twitter.com/realDonaldTrump/status/1333084257858834438", "https://twitter.com/realDonaldTrump/status/1332778938121203720") 
flagged_url <- c(flagged_url, "https://twitter.com/realDonaldTrump/status/1332776310196883461", "https://twitter.com/realDonaldTrump/status/1332552283553476608", "https://twitter.com/SenMastriano/status/1332398733401591808", "https://twitter.com/realDonaldTrump/status/1332407714304110597", "https://twitter.com/realDonaldTrump/status/1332380892682215424", "https://twitter.com/realDonaldTrump/status/1332352538855747584", "https://twitter.com/realDonaldTrump/status/1332349861774155778", "https://twitter.com/realDonaldTrump/status/1332337895584264197", "https://twitter.com/OANN/status/1331984934253125632", "https://twitter.com/OANN/status/1332002206208249856", "https://twitter.com/newsmax/status/1332264150312038400", "https://twitter.com/realDonaldTrump/status/1331987171700510720", "https://twitter.com/realDonaldTrump/status/1332317394165968899", "https://twitter.com/realDonaldTrump/status/1332317347722498048", "https://twitter.com/realDonaldTrump/status/1331987171700510720", "https://twitter.com/LLinWood/status/1331753058024517634", "https://twitter.com/realDonaldTrump/status/1331761131120103424", "https://twitter.com/Cernovich/status/1331707452304228352", "https://twitter.com/i/events/1308626736066617344", "https://twitter.com/replouiegohmert/status/1330606002299920387") 
flagged_url <- c(flagged_url, "https://twitter.com/realDonaldTrump/status/1331750037777510404", "https://twitter.com/realDonaldTrump/status/1331738816856666114", "https://twitter.com/realDonaldTrump/status/1331695288231333890", "https://twitter.com/realDonaldTrump/status/1331684437705302018", "https://twitter.com/realDonaldTrump/status/1331655154492448770", "https://twitter.com/Lrihendry/status/1331127441604145152", "https://twitter.com/realDonaldTrump/status/1331214247955738624", "https://twitter.com/LLinWood/status/1331315679321092097", "https://twitter.com/VicToensing/status/1329053473657249797", "https://twitter.com/VicToensing/status/1331249032006602753", "https://twitter.com/Lrihendry/status/1331390178624229376", "https://twitter.com/toddeherman/status/1331393990957047808", "https://twitter.com/justin_hart/status/1329886440449138689", "https://twitter.com/realDonaldTrump/status/1331393812728573952", "https://twitter.com/realDonaldTrump/status/1331225404351373313", "https://twitter.com/realDonaldTrump/status/1331219093563781122", "https://twitter.com/realDonaldTrump/status/1331214247955738624", "https://twitter.com/realDonaldTrump/status/1331086969183621120", "https://twitter.com/realDonaldTrump/status/1331057517095489539", "https://twitter.com/realDonaldTrump/status/1330737141794676736", "https://twitter.com/realDonaldTrump/status/1330732289018503170", "https://twitter.com/realDonaldTrump/status/1330367988621594625", "https://twitter.com/realDonaldTrump/status/1330555645213483016", "https://twitter.com/realDonaldTrump/status/1330487246236028935", "https://twitter.com/realDonaldTrump/status/1330137267680186371", "https://twitter.com/realDonaldTrump/status/1330374020613758977", "https://twitter.com/realDonaldTrump/status/1330367988621594625", "https://twitter.com/realDonaldTrump/status/1330368206968643584", "https://twitter.com/realDonaldTrump/status/1330368448552169474", "https://twitter.com/ChanelRion/status/1330196983966019586")
flagged_url <- c(flagged_url, "https://twitter.com/realDonaldTrump/status/1330351724553441282", "https://twitter.com/realDonaldTrump/status/1330351802508775426", "https://twitter.com/realDonaldTrump/status/1330327620148465664", "https://twitter.com/realDonaldTrump/status/1330325425667629058", "https://twitter.com/realDonaldTrump/status/1330323589170663426", "https://twitter.com/realDonaldTrump/status/1330319748660416513", "https://twitter.com/realDonaldTrump/status/1330259856662654978", "https://twitter.com/realDonaldTrump/status/1330248268656357376", "https://twitter.com/realDonaldTrump/status/1330137741078695939", "https://twitter.com/realDonaldTrump/status/1330137267680186371", "https://twitter.com/realDonaldTrump/status/1329963571250335744", "https://twitter.com/realDonaldTrump/status/1329963296854847492", "https://twitter.com/realDonaldTrump/status/1329963239170564098", "https://twitter.com/realDonaldTrump/status/1329871775707107335", "https://twitter.com/realDonaldTrump/status/1329871776889925636", "https://twitter.com/realDonaldTrump/status/1329784812257890306", "https://twitter.com/realDonaldTrump/status/1329780467663564806", "https://twitter.com/realDonaldTrump/status/1329761125404205057", "https://twitter.com/realDonaldTrump/status/1329760015314464770", "https://twitter.com/mtgreenee/status/1329261913834991616", "https://twitter.com/realDonaldTrump/status/1329298668403499009", "https://twitter.com/realDonaldTrump/status/1329521429575049231", "https://twitter.com/realDonaldTrump/status/1329478149609041927", "https://twitter.com/realDonaldTrump/status/1329459995893764102", "https://twitter.com/realDonaldTrump/status/1329424134166687744", "https://twitter.com/realDonaldTrump/status/1329405682706247683", "https://twitter.com/realDonaldTrump/status/1329401626763943936", "https://twitter.com/LizRNC/status/1329115371383697408")
flagged_url <- c(flagged_url, "https://twitter.com/realDonaldTrump/status/1329298668403499009", "https://twitter.com/realDonaldTrump/status/1329093126238203905", "https://twitter.com/realDonaldTrump/status/1329087255168708608", "https://twitter.com/realDonaldTrump/status/1329086548093014022", "https://twitter.com/realDonaldTrump/status/1329075487553974275", "https://twitter.com/realDonaldTrump/status/1329069814195871744", "https://twitter.com/realDonaldTrump/status/1329065945160175616", "https://twitter.com/realDonaldTrump/status/1329064787142172673", "https://twitter.com/realDonaldTrump/status/1329060562442067969", "https://twitter.com/realDonaldTrump/status/1329054683441278977", "https://twitter.com/realDonaldTrump/status/1328448530504163329", "https://twitter.com/realDonaldTrump/status/1328856932011167744", "https://twitter.com/realDonaldTrump/status/1328852352787484677", "https://twitter.com/realDonaldTrump/status/1328852354049957888", "https://twitter.com/realDonaldTrump/status/1328830381429288962")
flagged_url <- c(flagged_url, "https://twitter.com/realDonaldTrump/status/1328448530504163329", "https://twitter.com/realDonaldTrump/status/1328382287331856384", "https://twitter.com/realDonaldTrump/status/1328361451497664512", "https://twitter.com/realDonaldTrump/status/1328338241284616193", "https://twitter.com/realDonaldTrump/status/1328334945148952576", "https://twitter.com/alexbruesewitz/status/1327703244949377025", "https://twitter.com/alexbruesewitz/status/1327804135282978817", "https://twitter.com/realDonaldTrump/status/1328328547598000130", "https://twitter.com/realDonaldTrump/status/1328325907401093121", "https://twitter.com/realDonaldTrump/status/1328200072987893762", "https://twitter.com/kylenabecker/status/1327511568993701888", "https://twitter.com/realDonaldTrump/status/1328152465016020993", "https://twitter.com/realDonaldTrump/status/1328152466752491526", "https://twitter.com/realDonaldTrump/status/1328093294782509060", "https://twitter.com/realDonaldTrump/status/1327979630477922304")
flagged_url <-c(flagged_url, "https://twitter.com/realDonaldTrump/status/1327978710809661440", "https://twitter.com/GreggJarrett/status/1326250909282742276", "https://twitter.com/realDonaldTrump/status/1327960545929072645", "https://twitter.com/realDonaldTrump/status/1327958640309972992", "https://twitter.com/realDonaldTrump/status/1327956491056279552", "https://twitter.com/realDonaldTrump/status/1327952603318194178", "https://twitter.com/realDonaldTrump/status/1327750127679889409", "https://twitter.com/realDonaldTrump/status/1327708998662025216", "https://twitter.com/realDonaldTrump/status/1327717286778638340", "https://twitter.com/realDonaldTrump/status/1327717223142731779",
"https://twitter.com/realDonaldTrump/status/1327716728558772226", "https://twitter.com/realDonaldTrump/status/1327715767916392449", "https://twitter.com/realDonaldTrump/status/1327708998662025216", "https://twitter.com/realDonaldTrump/status/1327704841964183552", "https://twitter.com/realDonaldTrump/status/1327619653020110850", "https://twitter.com/realDonaldTrump/status/1327619654592892931", "https://twitter.com/realDonaldTrump/status/1327481814013906944")
flagged_url <- c(flagged_url, "https://twitter.com/DanScavino/status/1324578579250843648", "https://twitter.com/realDonaldTrump/status/1327438487537246210", "https://twitter.com/realDonaldTrump/status/1327413534901350400", "https://twitter.com/realDonaldTrump/status/1327103335195938817", "https://twitter.com/realDonaldTrump/status/1327407964404260870", "https://twitter.com/jmclghln/status/1326910605618503687", "https://twitter.com/realDonaldTrump/status/1327350069947936768", "https://twitter.com/realDonaldTrump/status/1327319294057848832", "https://twitter.com/realDonaldTrump/status/1327279929319432200", "https://twitter.com/realDonaldTrump/status/1327103335195938817", "https://twitter.com/realDonaldTrump/status/1327095398712946695", "https://twitter.com/realDonaldTrump/status/1326926226888544256", "https://twitter.com/ksorbs/status/1325176443215749121", "https://twitter.com/TrumpStudents/status/1326020907379400706", "https://twitter.com/realDonaldTrump/status/1326906607154900998", "https://twitter.com/realDonaldTrump/status/1326894138516774913", "https://twitter.com/realDonaldTrump/status/1326875863657361409", "https://twitter.com/realDonaldTrump/status/1326740844427304960", "https://twitter.com/TrumpWarRoom/status/1326721355107151872")
flagged_url <- c(flagged_url, "https://twitter.com/jonvoight/status/1326323889417322497", "https://twitter.com/realDonaldTrump/status/1326679385966047236", "https://twitter.com/realDonaldTrump/status/1326630618831130624", "https://twitter.com/realDonaldTrump/status/1326525851752656898", "https://twitter.com/realDonaldTrump/status/1326353226749386757", "https://twitter.com/realDonaldTrump/status/1326348976531136513", "https://twitter.com/realDonaldTrump/status/1326347841476890627", "https://twitter.com/realDonaldTrump/status/1326327582074220544", "https://twitter.com/realDonaldTrump/status/1326315284169445376", "https://twitter.com/realDonaldTrump/status/1326186297157963777", "https://twitter.com/realDonaldTrump/status/1326186126709821440", "https://twitter.com/realDonaldTrump/status/1325967327611981829", "https://twitter.com/realDonaldTrump/status/1325967220757966852", "https://twitter.com/realDonaldTrump/status/1325966661942435841")
```

```{r, function and get status ID}
get_status_id <- function(URL){
  #removing URL beginning
  URL <- str_split(URL, "status/")[[1]]
  #getting second half of split
  status_id <- tail(URL, 1)
  return(status_id)
}
flagged_status_id <- map_chr(flagged_url, get_status_id)
```


```{r, flagging data}
#Resaved to manipulate dataset
trump_tweets_total <- trump_tweets_997
trump_tweets_total <- trump_tweets_total %>%
  mutate("flag" = trump_tweets_total$status_id%in%flagged_status_id)%>%
  #reversee booleans for appearances - flagged AS true or AS false
  mutate("flag" = !flag)%>%
  #Select columns for analysis
  select(created_at, status_id, text, favorite_count, retweet_count, flag)
```

The second part is cutting off any extra tweets from the total data set if we are unable to check if they are flagged or not (Twitter will only allow users to view tweets posted 28 days earlier for @RealDonaldTrump). This second factor should be disregarded if researchers have access to all of @RealDonaldTrump's tweets and can account for flagged tweets prior to the 28 day mark.

```{r, cutting unchecked tweets}
#Get the last entry
last_flag <- tail(flagged_status_id, n=1)

#Get all data for last entry
last_created <- trump_tweets_total%>%
  filter(status_id == last_flag)

#Get date for last entry
last_created <- last_created$created_at

#filter out data created before last entry
trump_tweets_total <- trump_tweets_total%>%
  filter(created_at >= last_created)

#Save data
write.csv(trump_tweets_total, "Trump_Tweets_flagged_unflagged.csv")
```


```{r, daily time series}
ts_total <- trump_tweets_total%>%
  #Simplify date
  mutate(created_at = round_date(created_at, unit = "day"))%>%
  group_by(created_at, flag)%>%
  dplyr::count()

ts_day <- ggplot(ts_total, aes(x = created_at, fill = flag)) +
  geom_col(aes(y=n))+
  ylab("Number of Tweets")+#y label
  xlab("Time (Nov. 9th, 2020 - Dec. 7th, 2020)")+#x label
  ggtitle("Trump's Flagged vs. Unflagged Tweets Per Day (Stacked)")
ggsave(filename="time_series_day.png", plot=ts_day)#save to wd
```

```{r, weekly time series}
#Creating dataframe for ggplot
ts_week <- trump_tweets_total%>%
  #Simplify date
  mutate(created_at = round_date(created_at, unit = "week"))%>%
  group_by(created_at, flag)%>%
  dplyr::count()

#ggplot graph
ts_week <- ggplot(ts_week, aes(x = created_at, fill = flag)) +
  geom_col(aes(y=n))+
  ylab("Number of Tweets")+#y label
  xlab("Time (Nov. 9th, 2020 - Dec. 7th, 2020)")+#x label
  ggtitle("Trump's Flagged vs. Unflagged Tweets Per Week (Stacked)")
ggsave(filename="time_series_week.pdf", plot=ts_week) #save to wd
```

Now, retweets and favorites stuff:

```{r, popularity of tweets}
retwli_total <- trump_tweets_total%>%
  mutate(created_at = round_date(created_at, unit = "day"))%>%
  group_by(created_at, flag)%>%
  #Average count per day by favorites and retweets
  summarise(favorite_count = sum(favorite_count)/nrow(retwli_total),
         retweet_count = sum(retweet_count)/nrow(retwli_total))%>%
  #Added an extra column b/c will collapse with unite
  mutate(flag2 = flag) %>%
  gather(key = "retweet_fav", value = "count", -c(created_at, flag, flag2))%>%
  #Uniting for labels
  unite(col = "retweet_fav_flag", c(retweet_fav, flag2))

#GGplot
retwli <- ggplot(retwli_total, aes(x = created_at, y = count, group = interaction(retweet_fav_flag, flag), color = flag)) +
  geom_smooth()+
  xlab("Time (Nov. 9th, 2020 - Dec. 7th, 2020)")+#x label
  ylab("Number of Retweets or Favorites")+#y
  ggtitle("Retweets and Favorites of Flagged vs. Unflagged Trump Tweets Per Day")

#Labels failed

ggsave(filename="Retweets_faves_flagged_v_unflagged.pdf", plot=retwli)
```


Unique words study:
```{r, text frequency processing}
dtm <- trump_tweets_total%>%
  #Arrange it to sort and separate later
  arrange(desc(flag))%>% 
  select(text)#only interested in text

#For separate later
n_unflagged <- sum(trump_tweets_total$flag)
n_columns <- nrow(trump_tweets_total)

#preprocessing
dtm <- Corpus(VectorSource(dtm$text))
dtm <- DocumentTermMatrix(dtm,
           control = list(tolower = TRUE,
                          removePunctuation = TRUE,
                          removeNumbers = TRUE,
                          stopwords = TRUE,
                          stemming=TRUE))
dtm.m <- as.data.frame(as.matrix(dtm))
# These words are not important but get through preprocessing
dtm.m$this <- NULL 
dtm.m$has <- NULL
dtm.m$will <- NULL
dtm.m$get <- NULL
#also keeps retweets/hashtags

#Separation for counting
unflagged_words <- dtm.m[1:n_unflagged,]
flagged_words <- dtm.m[(n_unflagged+1):n_columns,]

# Subset into 2 DTMs, 1 for each speaker
#frequency per document becayse of large difference is number of tokens
unflagged_words <- colSums(unflagged_words)/nrow(unflagged_words) 
flagged_words <- colSums(flagged_words)/nrow(flagged_words)

#Get frequencies
freq <- flagged_words - unflagged_words

# Sort the words
freq <- sort(freq, decreasing = T)
```

```{r, Creating Wordcloud}
#Top words in flagged tweets
set.seed(123)#ensures reproducability
wordcloud(names(freq), freq, max.words=100, random.color = F, colors = (brewer.pal(8,"Dark2")))

# Top words in non-flagged tweets
set.seed(123)#ensures reproducability
wordcloud(names(freq), -freq, max.words=100, random.color = F, colors = (brewer.pal(8,"Dark2")))
#To print, run in RScript

#Warnings:
# realdonaldtrump could not be fit on page. It will not be plotted.
# senat could not be fit on page. It will not be plotted.
# counti could not be fit on page. It will not be plotted.
# new could not be fit on page. It will not be plotted.

```


